Impact of the 2016 Presidential Election on Urban Mobility: Who is Affected the Most?

### 2019-11-25 manuscript.Rmd
dc roads data added

```{r setup, include=FALSE}
library(tidyverse)
library(sf)
library(rgdal)
load("data/travel_times.RData")
theme_map <- theme_void()

travel_times <- travel_times %>%
	mutate(origin_id = factor(origin_id),
				 dest_id = factor(dest_id))
```

@@

```{r map}
travel_time_sf %>%
	ggplot() +
	geom_sf(mapping = aes(fill = mean_travel_time)) +
	theme_map +
	scale_fill_viridis_c(direction = -1)
```

>>>>

```{r setup, include=FALSE}
library(tidyverse)
library(sf)
library(rgdal)
library(tigris)
library(spdep)
library(sf)

load("data/travel_times.RData")
theme_map <- theme_void()

travel_times <- travel_times %>%
	mutate(origin_id = factor(origin_id),
				 dest_id = factor(dest_id))

head(travel_times)
```

```{r}
#tigris package - contains roads for DC
options(tigris_class="sf")
#primary_secondary_roads includes interstates and other highways in DC
dc_roads <- primary_secondary_roads(state="DC") %>%
	st_transform(crs = 102285)
```

@@

```{r map}
travel_time_sf %>% filter(year == 2017, month == 1, week == 3) %>%
	ggplot() +
	geom_sf(mapping = aes(fill = mean_travel_time)) +
	theme_map +
	scale_fill_viridis_c(direction = -1)

travel_time_sf %>% filter(year == 2017, month == 1, week == 4)%>%
	ggplot() +
	geom_sf(mapping = aes(fill = mean_travel_time)) +
	geom_sf(data = dc_roads) +
	theme_map +
	scale_fill_viridis_c(direction = -1)
```

```{r}
mean((travel_times %>% filter(year == 2017, month == 1, week == 3))$mean_travel_time)
```

```{r}
mean((travel_times %>% filter(year == 2016, month == 9, week == 3))$mean_travel_time)
```
